Learning to Group and Order AMR Semantics for General Purpose Discourse Planning

### 2015-12-10 paper/paper.tex
fix bib ordering
finished revisions through conclusion

@@

\begin{figure}
\begin{equation*}
\begin{split}
\exists s,d2,p2,c,n: &\\
&\text{instance}(s,seize\text{-}01) \wedge \text{instance}(d2, drug) \wedge \\
&\text{instance}(p2, prosecutor) \wedge \text{instance}(c, country) \wedge \\
&\text{instance}(n, name) \wedge \text{arg0}(s,p2) \wedge \text{arg1}(s,d2)
\wedge \\ &\text{arg2}(s,c) \wedge \text{name}(c,n) \wedge \text{op1}(n,
``South") \wedge \\ &\text{op2}(n, ``Korea") \wedge \text{unit}(d2, kilogram)
\wedge \text{quant}(d2, 80)
\end{split}
\end{equation*}
\label{fig:amr_example_logical}
\caption{Example AMR in Logical Form}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{amr_example.pdf}
\label{fig:amr_example}
\caption{Example AMR in Graphical Form}
\end{figure}

@@

To contsruct the entire pipeline, we trained a subgraph selector and subgraph
ordeer separately and combined them in the following manner:

@@

To evaluate the pipeline as a whole, we used a revised Kendall's tau metric, in
accordance with \cite{lapata2006automatic}. To score both the selection and
ordering simultaneously, we count the number of facts which are out of order.
This accounts for mistakes both in the subgraph selection, where a fact is
placed in the wrong set of facts, and in the subgraph ordering, where a group
of facts is placed in the wrong order.

@@

We trained a subgraph selector and orderer on our training dataset and
constructed a pipeline as described above. To establish a baseline, we ran the
pipeline against our test set, but rather than perform discrete optimization,
each optimizer just computed a random sampling of the possible partitionings or
orderings.

Next, we ran the pipeline again, this time using our discrete optimizations.
We implemented only greedy search for the subgraph selection problem, but used
both greedy search and simulated annealing for the subgraph ordering problem.

@@

\begin{table}[H]
\centering
\caption{Revised Kendall Tau Results}
\label{tab:experiments}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean} & \textbf{Std. Dev.} & \textbf{Min} & \textbf{Max} \\ \midrule
Baseline, Baseline & 40.967289719626166 & 62.38075619228794 & 0 & 634 \\
Greedy, Greedy & 36.434579439252339 & 61.217880539269935 & 2 & 563 \\
Greedy, Annealing & 34.481308411214954 & 50.605189107869165 & 2 & 411 \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Mean number of sentences and facts per sentence for the pipeline}
\label{tab:metrics}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean \# of Sentences} & \textbf{Mean \#
of Facts per Sentence} \\ \midrule
Baseline, Baseline & 6.1074766355140184 & 2.3297628156082633 \\
Greedy, Greedy & 5.8130841121495331 & 2.447749196141479 \\
Greedy, Annealing & 5.8130841121495331 & 2.447749196141479 \\ \bottomrule
\end{tabular}
\end{table}

@@

(1) The evaluation of system such as this ultimately needs to have human involvement, with subjective scoring done by native English speakers. The learned scorers seek to find information groupings and orderings that match those of the input texts; however there is not reason to believe that other groupings/orderings are incorrect or worse. The difficulty in this process is that understanding the semantics of an AMR paragraph and an AMR sentence is a non-trivial task for a human-scorer. These graphs could have hundreds of nodes and edges, representing complex higher-order logic. Without an NLG system built upon AMR semantics it will be incredibly time-consuming for a human annotator. We may be able to build a tool that translates AMR to a more easily understandable language, without having to generate all the way to natural language, allowing more rapid human scoring.

(2) In our system, information grouping and ordering are treated as separate systems in a pipeline; however, these two tasks should really happen simultaneously in one step. The ordering of information is clearly dependent on how the information is grouped, and the information grouped in a sentence should be dependent on what has already been said (the ordering of sentences beforehand). Since these two tasks are dependent on each other, we expect a simultaneous system would outperform our pipeline architecture.

>>>>

\begin{figure}
\begin{equation*}
\begin{split}
\exists s,d2,p2,c,n: &\\
&\text{instance}(s,seize\text{-}01) \wedge \text{instance}(d2, drug) \wedge \\
&\text{instance}(p2, prosecutor) \wedge \text{instance}(c, country) \wedge \\
&\text{instance}(n, name) \wedge \text{arg0}(s,p2) \wedge \text{arg1}(s,d2)
\wedge \\ &\text{arg2}(s,c) \wedge \text{name}(c,n) \wedge \text{op1}(n,
``South") \wedge \\ &\text{op2}(n, ``Korea") \wedge \text{unit}(d2, kilogram)
\wedge \text{quant}(d2, 80)
\end{split}
\end{equation*}
\caption{Example AMR in Logical Form}
\label{fig:amr_example_logical}
\end{figure}

\begin{figure}
\includegraphics[width=\linewidth]{amr_example.pdf}
\caption{Example AMR in Graphical Form}
\label{fig:amr_example}
\end{figure}

@@

@@

To construct the entire pipeline, we trained the subgraph selector and subgraph
orderer separately and combined them via Algorithm \ref{pipeline_procedure}.

@@

To evaluate the pipeline as a whole, we used a revised Kendall's tau metric. 
To score both the selection and ordering simultaneously, we count the number of facts which are out of order.
This accounts for mistakes both in the subgraph selection, where a fact is
placed in the wrong sentence, and in the subgraph ordering, where a sentence
is placed in the wrong order.

@@

We trained the subgraph selector and orderer on our training dataset and
constructed a pipeline as described in Algorithm \ref{pipeline_procedure}.
To establish a baseline, we ran the
pipeline against our test set, but rather than perform discrete optimization,
each optimizer used a random sampling from the possible partitions and 
orderings respectively.

Next, we ran the pipeline again, this time using our discrete optimizations.
We implemented only greedy search for the subgraph selection problem, but ran experiments with
both greedy search and simulated annealing for the subgraph ordering problem.

@@

\begin{table}[H]
\centering
\caption{Revised Kendall Tau Results}
\label{tab:experiments}
\begin{tabular}{@{}lllll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean} & \textbf{Std. Dev.} & \textbf{Min} & \textbf{Max} \\ \midrule
Baseline, Baseline & 40.97 & 62.38 & 0 & 634 \\
Greedy, Greedy & 36.43 & 61.22 & 2 & 563 \\
Greedy, Annealing & 34.48 & 50.60 & 2 & 411 \\ \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\caption{Mean number of sentences and facts per sentence for the pipeline}
\label{tab:metrics}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{(Selection, Ordering)} & \textbf{Mean \# Sentences} & \textbf{Mean \# Facts per Sentence} \\ \midrule
Baseline, Baseline & 6.11 & 2.33 \\
Greedy, Greedy & 5.81 & 2.45\\
Greedy, Annealing & 5.81 & 2.45 \\ \bottomrule
\end{tabular}
\end{table}

@@

(1) The evaluation of system such as this ultimately needs to have human involvement, with subjective scoring done by native English speakers. The learned scorers seek to find information groupings and orderings that match those of the input texts; however there is no reason to believe that other groupings/orderings are incorrect. The difficulty in this process is that understanding the semantics of an AMR paragraph a non-trivial task for a human-scorer. These graphs could have hundreds of nodes and edges, representing complex higher-order logic. Without an NLG system built upon AMR semantics it will be incredibly time-consuming for a human annotator. We may be able to build a tool that translates AMR to a more easily understandable language, without having to generate all the way to natural language, allowing more rapid human scoring.

(2) In our system, information grouping and ordering are treated as separate systems in a pipeline; however, these two tasks should really happen simultaneously. The ordering of information is clearly dependent on how the information is grouped, and the information grouped in a sentence should be dependent on what has already been said (the ordering of sentences beforehand). Since these two tasks are interdependent, we expect a simultaneous system would outperform our pipeline architecture.
